---
title: "Group Assignment #9"
Authors: "Lynsey Keator, Artie Maharaj, Rebecca Neal, Hongxiao Yu"
Date: "April 14, 2020"
output: html_notebook
---
In this study we want to determine for women who suffered childhood physical abuse, is there a difference in the average PTSD scores of women who also suffered childhood sexual abuse and those who did not suffer childhood sexual abuse, after accounting for the severity of the childhood physical abuse? 

```{r include=FALSE}

library(tidyverse)
library(here)

abuse <- read_csv("Sexual Abuse Data.csv")

```


### Set up Q1 side by side box plots of explanatory variable (csa) to response
### variable (ptsd)

```{r}
ggplot(abuse, aes(x = csa, y = ptsd))+
         geom_boxplot()+
         labs(x = "Childhood Sexual Abuse", 
              y = "PTSD Scale",
              title = "Relationship of Childhood Abuse to PTSD")
```

### Q2 Descriptive statistics for the response variable (ptsd) at each level 
### of the categorical variable (csa)
```{r}
tapply(abuse$ptsd, abuse$csa, summary)
```

### Q3 side by side box plots of the covariate (cpa) to the explanatory 
### variable (csa)

```{r}
ggplot(abuse, aes(x = csa, y = cpa))+
         geom_boxplot()+
         labs(x = "Childhood Sexual Abuse", 
              y = "Childhood Physical Abuse Scale",
              title = "Relationship of Childhood Abuse to Childhood Physical 
              Abuse Scale")
```