---
title: "Group Assignment #9"
Authors: "Lynsey Keator, Artie Maharaj, Rebecca Neal, Hongxiao Yu"
Date: "April 14, 2020"
output: html_notebook
---
In this study we want to determine for women who suffered childhood physical abuse, is there a difference in the average PTSD scores of women who also suffered childhood sexual abuse and those who did not suffer childhood sexual abuse, after accounting for the severity of the childhood physical abuse? 

```{r include=FALSE}

library(tidyverse)
library(here)

abuse <- read_csv("Sexual Abuse Data.csv")

```


### Set up Q1 side by side box plots of explanatory variable (csa) to response
### variable (ptsd)

```{r}
ggplot(abuse, aes(x = csa, y = ptsd)) +
  geom_boxplot()+
   labs(x = "Childhood Sexual Abuse",
       y = "PTSD Scale",
       title = "Relationship of Childhood Abuse to PTSD")

```

### 7 Calculate the residuals when modeling the response variable as a function 
# of the explanatory variable and covariate (without interaction) and then create a 
# Q-Q plot of the residuals to confirm the condition of a normal distribution.

```{r}
model2 <- abuse$ptsd ~ abuse$cpa + abuse$csa
model2.out <- lm(model2)
ggplot(model2.out, aes(sample = rstandard(model2.out))) +
  stat_qq() +
  stat_qq_line() +
  labs(x = "Theoretical Quantiles", y = "Sample Quantiles")
```


### 8. Illustrate the relationship of the explanatory variable to the response variable 
# after accounting for the covariate by constructing a scatterplot with 
# separate regression lines for each level of the explanatory variable.

```{r}
ggplot(data = abuse, mapping = aes(x = cpa, y = ptsd, color = csa)) +
  geom_point() +
  labs(x = "Childhood Physical Abuse Scale",
       y= "PTSD score",
       title = "Association between PTSD score and Childhood Physical Abuse Scale",
       color = "CSA") +
  stat_smooth(method = "lm") +
   scale_color_discrete(labels=c('Abused', 'Not Abused'))
```


# 9. Construct the ANCOVA table after modeling the response variable as a function 
# of the explanatory variable and covariate (without interaction).
```{r}
model2.out
```


